UN

### 2020-11-18 src/un.Rmd
S1

@@

@@

@@

# This are just asearches in the world bank database

@@

# TODO: GAPS
```

@@

```{r}
data <- list(zipf, rhs1, net, bb, mobile, fixed)# tele.emp and tv are not used in the regressions
sapply(data, function(x) dim(x))
sapply(data, function(x) names(x))
sapply(data, function(x) str(x))

>>>>

library(REAT)

@@

Add description

@@

## Alternative measures of spatial dispertion

```{r}
gini <- urban.pop %>% 
  rename(country = ISO) %>%
  dplyr::select((contains("pop")) | country) %>%
  group_by(country) %>% 
  summarise(across(everything(), list(REAT::gini))) %>%
  pivot_longer(!country, names_to = "year", values_to = "gini") %>%
  mutate(year = gsub("pop", "", year)) %>% 
  mutate(year = str_sub(year, end=-3)) %>%
  mutate(year = as.numeric(year))

herf <- urban.pop %>% 
  rename(country = ISO) %>%
  dplyr::select((contains("pop")) | country) %>%
  group_by(country) %>% 
  summarise(across(everything(), list(REAT::herf))) %>%
  pivot_longer(!country, names_to = "year", values_to = "herf") %>%
  mutate(year = gsub("pop", "", year)) %>% 
  mutate(year = str_sub(year, end=-3)) %>%
  mutate(year = as.numeric(year))

cv <- urban.pop %>% 
  rename(country = ISO) %>%
  dplyr::select((contains("pop")) | country) %>%
  group_by(country) %>% 
  summarise(across(everything(), list(EnvStats::cv))) %>% # raster::cv / 100
  pivot_longer(!country, names_to = "year", values_to = "cv") %>%
  mutate(year = gsub("pop", "", year)) %>% 
  mutate(year = str_sub(year, end=-3)) %>%
  mutate(year = as.numeric(year))

@@

# These are just searches in the world bank database

@@

@@

```{r}
data <- list(zipf, rhs1, net, bb, mobile, fixed,
             gini, herf, cv)# tele.emp and tv are not used in the regressions
sapply(data, function(x) dim(x))
sapply(data, function(x) names(x))
sapply(data, function(x) str(x))
